Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-07 paper.qmd
Updated Figure 10

@@

error_two_non_linear_diff_shaped_close_clusters_umap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_umap.rds")
error_two_non_linear_diff_shaped_close_clusters_tsne <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_tsne.rds")
error_two_non_linear_diff_shaped_close_clusters_phate <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_phate.rds")
error_two_non_linear_diff_shaped_close_clusters_trimap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_trimap.rds")
error_two_non_linear_diff_shaped_close_clusters_pacmap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_pacmap.rds")

error_two_non_linear_diff_shaped_close_clusters <- bind_rows(error_two_non_linear_diff_shaped_close_clusters_umap, 
                         error_two_non_linear_diff_shaped_close_clusters_tsne,
                         error_two_non_linear_diff_shaped_close_clusters_phate,
                         error_two_non_linear_diff_shaped_close_clusters_trimap,
                         error_two_non_linear_diff_shaped_close_clusters_pacmap)

@@

error_plot_two_non_linear_diff_shaped_close_clusters <- ggplot(error_two_non_linear_diff_shaped_close_clusters, 
                           aes(x = a1, 
                               y = MSE, 
                               colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_two_non_linear_diff_shaped_close_clusters$a1))[seq(1, length(unique(error_two_non_linear_diff_shaped_close_clusters$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#ff7f00','#4daf4a', "#a65628",'#636363')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

@@

free(error_plot_two_non_linear_diff_shaped_close_clusters) + wrap_plots(nldr_two_non_linear_diff_shaped_close_clusters1, nldr_two_non_linear_diff_shaped_close_clusters2, nldr_two_non_linear_diff_shaped_close_clusters3, 
                                    nldr_two_non_linear_diff_shaped_close_clusters4, nldr_two_non_linear_diff_shaped_close_clusters5, ncol = 2)
```

>>>>

tsne_two_non_linear_diff_shaped_close_clusters <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_tsne_perplexity_62.rds")

nldr_two_non_linear_diff_shaped_close_clusters6 <- tsne_two_non_linear_diff_shaped_close_clusters |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  interior_annotation("f", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

@@

error_two_non_linear_diff_shaped_close_clusters_umap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_umap.rds")
error_two_non_linear_diff_shaped_close_clusters_tsne <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_tsne.rds")
error_two_non_linear_diff_shaped_close_clusters_phate <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_phate.rds")
error_two_non_linear_diff_shaped_close_clusters_trimap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_trimap.rds")
error_two_non_linear_diff_shaped_close_clusters_pacmap <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_pacmap.rds")
error_two_non_linear_diff_shaped_close_clusters_tsne2 <- read_rds("data/two_non_linear_diff_shaped_close_clusters/error_two_non_linear_diff_shaped_close_clusters_tsne2.rds")

error_two_non_linear_diff_shaped_close_clusters_tsne2 <- error_two_non_linear_diff_shaped_close_clusters_tsne2 |>
  mutate(method = "tSNE2")

error_two_non_linear_diff_shaped_close_clusters <- bind_rows(error_two_non_linear_diff_shaped_close_clusters_umap, 
                         error_two_non_linear_diff_shaped_close_clusters_tsne,
                         error_two_non_linear_diff_shaped_close_clusters_phate,
                         error_two_non_linear_diff_shaped_close_clusters_trimap,
                         error_two_non_linear_diff_shaped_close_clusters_pacmap,
                         error_two_non_linear_diff_shaped_close_clusters_tsne2)

@@

error_plot_two_non_linear_diff_shaped_close_clusters <- ggplot(error_two_non_linear_diff_shaped_close_clusters, 
                           aes(x = a1, 
                               y = MSE, 
                               colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_two_non_linear_diff_shaped_close_clusters$a1))[seq(1, length(unique(error_two_non_linear_diff_shaped_close_clusters$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#ff7f00','#4daf4a', "#a65628",'#636363', '#984ea3')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

@@

free(error_plot_two_non_linear_diff_shaped_close_clusters) + wrap_plots(nldr_two_non_linear_diff_shaped_close_clusters1, nldr_two_non_linear_diff_shaped_close_clusters2, nldr_two_non_linear_diff_shaped_close_clusters3, 
                                    nldr_two_non_linear_diff_shaped_close_clusters4, nldr_two_non_linear_diff_shaped_close_clusters5,
                                    nldr_two_non_linear_diff_shaped_close_clusters6, ncol = 2)
```
